Transcriptional dynamics of influenza virus infection in single cells

### 2017-08-25 paper/paper.tex
Changed Figure 1 to remove acronyms. Changed Figure 2A axis to reflect text. Added flow cytometry data for Figure 2B to supplement. Changed a few typosin text and changed title of subsection

\begin{figure}
\centerline{\includegraphics[width=0.7\linewidth]{figures/Validating_barcode_virus/validating_populations_D02.pdf}}
\caption{\label{fig:viruspopulations} The viral stocks in our experiments are relatively pure of defective particles. 
{\bf (A)}
Our viral stocks have a higher ratio of infectious particles to HA virion RNA compared to a high-defective stock propagated at high MOI.
HA viral RNA was quantified by qPCR on virions. 
{\bf (B)} 
Our viral stocks have a higher ratio of infectious particles to particles capable of expressing the viral HA protein.
A549 cells were infected with all three viral stocks at an MOI of 0.1, and the percentage of cells expressing HA protein at 9 hours post-infection was quantified by antibody staining and flow cytometry.
{\bf (C)} 
Our viral stocks are less immunostimulatory than virus propagated at high MOI. 
Measurements of \textit{IFNB1} transcript by qPCR normalized to the housekeeping gene L32 in A549 cells at 10 hours post infection at an MOI of 0.5.
MOIs were calculated by TCID50 on MDCK-SIAT1 cells.}
\figsupp[Flow cytometry data for calculating the percentage of HA-expressing cells.]{Longer caption}{\emph{HA-expression flow cytometry supplemental figure needs to be created.}}
\end{figure}

@@

Many of the genes that exhibit increased expression in cells with large amounts of viral mRNA are known or suspected to be regulated by the Nrf2 master regulator in response to oxidative stress.
These genes produce proteins that are involved in detoxification of reactive oxygen species or resultant products, the management of misfolded proteins, the electron transport chain, or a general stress response (Figure~\ref{fig:cellulargenes}~Figure~supplement~\ref{figsupp:ROStable}). 
We additionally see reduced expression of the nitric oxide synthase interacting protein (NOSIP). 
Transient oxidative stress to occur during virus infection, and may act in a proviral fashion via MAPK activation driving vRNP export.
The antioxidant response is thought to be largely antiviral, potentially through inhibition of MAPK activity.
Our data do not reveal whether the expression of genes involved in the response to oxidative stress are a cause or a symptom of higher levels of viral mRNA, and further investigation of this topic is an interesting area for future work.
Overall, the expression of some of the host genes in Figure~\ref{fig:cellulargenes}, along with inherent stochasticity and specific mutations to viral genes in individual cells, probably explain most of the variation in viral mRNA levels observed across the infected cells in our dataset.

>>>>

\begin{figure}
\centerline{\includegraphics[width=0.7\linewidth]{figures/Validating_barcode_virus/validating_populations_D02.pdf}}
\caption{\label{fig:viruspopulations} The viral stocks in our experiments are relatively pure of defective particles. 
{\bf (A)}
Our viral stocks have a higher ratio of infectious particles to HA virion RNA compared to a high-defective stock propagated at high MOI.
HA viral RNA was quantified by qPCR on virions. 
{\bf (B)} 
Our viral stocks have a higher ratio of infectious particles to particles capable of expressing the viral HA protein.
A549 cells were infected with all three viral stocks at an MOI of 0.1, and the percentage of cells expressing HA protein at 9 hours post-infection was quantified by antibody staining and flow cytometry.
{\bf (C)} 
Our viral stocks are less immunostimulatory than virus propagated at high MOI. 
Measurements of \textit{IFNB1} transcript by qPCR normalized to the housekeeping gene L32 in A549 cells at 10 hours post infection at an MOI of 0.5.
MOIs were calculated by TCID50 on MDCK-SIAT1 cells.}
\figsupp[Full flow cytometry data for panel B . \label{figsupp:HAstain}]{
Full flow cytometry date for  Figure~\ref{fig:viruspopulations}B. All populations infected at an MOI of 0.1 as calculated by TCID50 on MDCK-SIAT1 cells. 
{\bf (A)} Uninfected gating control
{\bf (B)} Cells infected with wild-type virus
{\bf (C)} Cells infected with synonymously barcoded virus
{\bf (D)} Cells infected with a stock of wild-type virus propagated at a high MOI, therefore enriched in defective virus.
}{\includegraphics[width=0.7\linewidth]{figures/Validating_barcode_virus/HA_stain_supplement.png}}\end{figure}

@@

Many of the genes that exhibit increased expression in cells with large amounts of viral mRNA are known or suspected to be regulated by the Nrf2 master regulator in response to oxidative stress.
These genes produce proteins that are involved in detoxification of reactive oxygen species or resultant products, the management of misfolded proteins, the electron transport chain, or a general stress response (Figure~\ref{fig:cellulargenes}~Figure~supplement~\ref{figsupp:ROStable}). 
We additionally see reduced expression of the nitric oxide synthase interacting protein (NOSIP). 
Transient oxidative stress is known to occur during viral infection, and may act in a proviral fashion via MAPK activation driving vRNP export.
The antioxidant response is thought to be largely antiviral, potentially through inhibition of MAPK activity.
Our data do not reveal whether the expression of genes involved in the response to oxidative stress are a cause or a symptom of higher levels of viral mRNA, and further investigation of this topic is an interesting area for future work.
Overall, the expression of some of the host genes in Figure~\ref{fig:cellulargenes}, along with inherent stochasticity and specific mutations to viral genes in individual cells, probably explain most of the variation in viral mRNA levels observed across the infected cells in our dataset.
